\documentclass{report}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{titletoc}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{pink}{rgb}{1,0.07,0.57}


\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{blue},
  keywordstyle=\color{pink},
  commentstyle=\color{dkgreen},
  stringstyle=\color{blue},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

\lstset{language=Java}

\title{Secure Coding - Team 7- Phase 5}
\author{Magnus Jahnen, Thomas Krex, Elias Tatros}
\date{\today}


\begin{document}

\maketitle

\part{Executive Summary}

This is the final report for the Secure Coding bank web application project of Team 7. In the semester we had to develop a common bank web software with different user roles, transactions of money with different TAN methods and batch transaction via file upload.

The bank application was tested by two other teams. The aim of the tests was to find security vulnerabilities. After each test we fixed all vulnerabilities the team or we ourselves have found. As a plus we implemented new features or fixed other non security related bugs.

This final report first describes the architecture of our application. After that there is a brief overview of the security measures our system offers. The last part describes the recent fixes we have implemented.

\tableofcontents

\part{Time Tracking Table}
\include{time_tracking_table}


\part{Application Architecture}
\include{architecture}

\part{Security Measures}
\include{security_measures}


\part{Fixes}
\include{hsts_fix}
\include{secure_cookie_fix}
\include{fix_process_timing}
\include{fix_tan_generation}
\include{fix_upload}
\include{lock_out}
\include{security_question}
\include{csrf}

\end{document}